---
title: "citizensci_setup"
author: "Fanglin"
date: "2023-12-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. Setup a citizensci project

AMMonitor 1.0.0 is a R package and can be act as a template for citizen science. It includes additional cloud storage options, a Shiny front end for running analyses, tagging photos and recording media, and interacting with the database. we can install it by performing the code:

```{r echo=TRUE}
# library(devtools)
# devtools::install_git(url = "https://code.usgs.gov/vtcfwru/ammonitor")
# browseURL(paste0(find.package("AMMonitor"), "/extdata/wiki/00-preface.html"))
# browseURL(paste0(find.package("AMMonitor"), "/extdata/wiki/01-introduction.html"))
browseURL(paste0(find.package("AMMonitor"), "/extdata/wiki/02-database.html"))
browseURL(paste0(find.package("AMMonitor"), "/extdata/wiki/03-people.html"))
```

The function ammCreateDirectories() will run to set up a monitoring program with AMMonitor. The code below illustrates how to set up a primary directory called citizensci in a directory called Dropbox.

```{r}
library(AMMonitor)
# # Create the AMMonitor directory structure
# ammCreateDirectories(amm_dir_name = "citizensci", 
#                      parent_path = "~/Dropbox")
# List the files created
list.files("~/Dropbox/citizensci")
```
There are the following subdirectories:

- ammls: Stores models in an AMModels library. Models are used throughout the AMMonitor process.
- database: Stores the AMMonitor SQLite database.
- log_drop: Stores incoming logs generated from audio equipment.
- logs: Stores archived logs tracking audio performance.
- motion_drop: Stores incoming photos triggered by a motion-detection.
- motion: Stores motion-triggered events.
- photo_drop: Stores incoming photos collected as timed events.
- photos: Stores archived photos collected as timed events.
- recording_drop: Stores incoming audio recording files (e.g.,.wav) captured in acoustic monitoring programs.
- recordings: Stores archived audio recording files (e.g., .wav)
captured in acoustic monitoring programs.
- scripts. Stores R scripts that can be sourced each day to automatically process new data.
- settings: Stores files needed to access accounts (e.g., Google
or Dropbox) via R.
- spatials: Stores spatial layers associated with locations in a
monitoring program (rasters and/or shapefiles) as RDS files.

Next, we use the AMModels function amModelLib() to create four separate model libraries. amModelLib() requires only a description field, but additional metadata may also be included:

```{r}
library(AMModels)
# help("AMModels") # look at the AMModels help page
# Create a  library called "activity"
activity <- AMModels::amModelLib(description = "This library stores models that predict activity-specific patterns.")

# Create a library called  classifiers 
classifiers <- AMModels::amModelLib(description = "This library stores machine learning models that predict a signal emitted from an object.")

# Create a  library called soundscape
soundscape <- AMModels::amModelLib(description = "This library stores results of a soundscape analysis.")

# Create a library called do_fp
do_fp <- AMModels::amModelLib(description = "This library stores results of analyses that can handle false positive detections.")

# Create a list of metadata to be added to each library
info <- list(PI = 'Fanglin Liu', 
             Organization = 'Hefei Institutes of Physical Science')

# Add metadata to each library
ammlInfo(activity) <- info
ammlInfo(classifiers) <- info
ammlInfo(soundscape) <- info
ammlInfo(do_fp) <- info

# Look at one of the libraries
activity
```

For now, we simply need to save the libraries to our ammls directory.

```{r}
# Save the libraries to the amml folder
saveRDS(object = activity, file = "ammls/activity.RDS")
saveRDS(object = classifiers, file = "ammls/classifiers.RDS")
saveRDS(object = soundscape, file = "ammls/soundscape.RDS")
saveRDS(object = do_fp, file = "ammls/do_fp.RDS")
```

At this point, we have 1) created a file directory required by citizensci, and 2) created four AMModels libraries in the ammls directory. 

## 2. 


